---
title: "Stat-Inference Assignment-02"
author: "Vinsent P."
date: "September 26, 2015"
output: pdf_document
---
  
  ## Objective: Going to analyze the ToothGrowth data in the R datasets package. 
  ### 1. Load the ToothGrowth data and perform some basic exploratory data analyses 
  ### 2. Provide a basic summary of the data.
  ### 3. Use confidence intervals and/or hypothesis tests to compare tooth growth by supp and dose. (Only use    ### techniques from class, even if there's other approaches worth considering)
  ### 5. State your conclusions and the assumptions needed for your conclusions.
  
```{r echo = TRUE}
library(ggplot2)  

### Load the dataset
data(ToothGrowth)

```
###Explore the Data
```{r}
head(ToothGrowth)
summary(ToothGrowth)


# visualize the data
qplot(dose,len,data=ToothGrowth, col=supp, main="Tooth length of guinea pigs by supplement type and dosage (mg)",xlab="Dosage (mg)", ylab="Tooth length") + geom_boxplot(aes(fill = supp))
```
##Hypothesis Testing

###H0: There is no significant difference in treatment from both the medicine OJ and VC
###H1: alternate of H0

###Tooth length in VC = OJ   H0
###Tooth length in VC NOT equal to OJ treaments

###Split the two treatment groups
```{r}
OJ = ToothGrowth$len[ToothGrowth$supp == 'OJ']
VC = ToothGrowth$len[ToothGrowth$supp == 'VC']
```

## T- Test

### one tail test


```{r}
t.test(OJ, VC, alternative = "greater", paired = FALSE, var.equal = FALSE, conf.level = 0.95)
```

###Hypothesis for dosage

###HO: there is no sifnificant difference in dosage in two sizes
###H1: There is difference in the two dosage
```{r}

##Divide the dataset with dosage group

OJ2 = ToothGrowth$len[ToothGrowth$supp == 'OJ' & ToothGrowth$dose == 2]
VC2 = ToothGrowth$len[ToothGrowth$supp == 'VC' & ToothGrowth$dose == 2]

half = ToothGrowth$len[ToothGrowth$dose == 0.5]
one = ToothGrowth$len[ToothGrowth$dose == 1]
two = ToothGrowth$len[ToothGrowth$dose == 2]


# T-test

##One-tailed independent t-test with unequal variance.

t.test(half, one, alternative = "less", paired = FALSE, var.equal = FALSE, conf.level = 0.95)


```
## p-value = 6.342e-08 is less than the 5% significance level .05 Hence accepting the Alternate hypothesis as there is difference in tooth growth.


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
